Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-16 TEBenchmarkPaper/article.tex
Abstract

\begin{abstract}
  We propose a benchmark suite for evaluating the efficiency and effectiveness
  of \emph{conjecture formation} by automated tools for \emph{mathematical
    theory exploration} in higher-order, inductive theories; a domain especially
  suited for analysing software. By providing standard tools and metrics, we
  hope to encourage innovation and comparison between the disparate approaches
  currently being pursued, and spur improvements similar to those seen in the
  competitive field of automated theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\begin{abstract}
  We propose a benchmarking methodology to evaluate the efficiency and quality
  of \emph{conjecture generation} by automated tools for \emph{mathematical
    theory exploration}. Our approach uses widely available theorem proving
  tasks as a \emph{ground-truth} corpus, and we demonstrate its use on the
  QuickSpec and IsaCoSy tools, finding that the former takes significantly less
  time to produce significantly more ``interesting'' output. By providing a
  standard, cross-tool evaluation technique we hope to encourage innovation and
  comparison between the disparate approaches currently being pursued, and spur
  improvements similar to those seen in the competitive field of automated
  theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
